---
title: 'charr - character operators 4 R'
date: 'March 28, 2017'
output: github_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo=T, comment=NA)
source('https://github.com/chiefBiiko/charr/raw/master/charr.R')
```

R is a lovely programming language. Nonetheless, working with strings in R can be a little cumbersome. <code>charr</code> attempts to make working with strings and characters in R as easy as ABC.

***

## Operators

| Name              | Purpose            | Usage                                        |
|-------------------|--------------------|----------------------------------------------|
|<code>%+%</code>   | Concatenation      | <code>'sakawa' %+% ' spirit'</code>          |
|<code>%r%</code>   | Repetition         | <code>'Hi' %r% 10</code>                     |
|<code>%i%</code>   | Getting characters | <code>'Fraudulent Activities' %i% 1:5</code> |
|<code>%i=%</code>  | Setting characters | <code>'King' %i=% c(2, 'o')</code>           |
|<code>%ii=%</code> | Insertion          | <code>'abc' %ii=% c(1:2, c('.', '.'))</code> |

***

## Using charr
<code>source('https://github.com/chiefBiiko/charr/raw/master/charr.R')</code>

***

## Character concatenation

Concatenate length 1 character vectors with the <code>%+%</code> operator:

```{r}
z <- ' makes lucky'
'sakawa' %+% ' spirit' %+%  z
```

***

## Character repetition

Repeat length 1 character vectors with the <code>%r%</code> operator:

```{r}
'saka' %r% 2
'Enter the secret' %+% ('!' %r% 10)
```

***

## Character subsetting

Subset length 1 character vectors with the indices of its characters using the <code>%i%</code> and <code>%i=%</code> operators. The former performs a get operation whereas the latter performs a set operation.

> The <code>%i=%</code> and <code>%ii=%</code> operators map their input string according to their right operand and return the resulting string. Thus, to really perform a *set* operation on an existing string variable one has to reassign the return value of the corresponding operator.

### Getting characters

Get characters of a length 1 character vector using the <code>%i%</code> operator:

```{r}
'Fraudulent Activities' %i% 1:5
x <- 'Get rid of dumb characters' %i% -c(12:16)
print(x)
```

In order to erase characters wrap their indices in <code>c()</code> prefixed with a minus sign. If the supplied subset indices are out of bounds (exceed the number of characters of the left operand) the return value contains all characters from the supplied start index until the end of the input string.

### Setting characters

Set characters of a length 1 character vector using the <code>%i=%</code> operator:

```{r}
'HELLO WORLD' %i=% c(7:11, rep('Y', 5))
y <- 'no money no funny'
y <- y %i=% c(c(1, 13:17), c('N', rep('X', 5)))
print(y)
```

The right operand must be a length 2 vector supplying a vector of replacement indices as first item and a vector of replacement values as second item. Note that the replacement indices are matched to the replacement values from left to right. Therefore, the number of replacement indices must equal the number of replacement values. Each replacement value must be a single character.

***

## Character insertion

Insert characters *after* specified indices into a length 1 character vector using the <code>%ii=%</code> operator:

```{r}
'HELLO WORLD' %ii=% c(c(5, 11), c(',', '!!!'))
abc <- 'ABC' %ii=% c(1:2, c('|', '|'))
print(abc) 
```

The right operand must be a length 2 vector supplying a vector of indices after which to insert strings as first item and a vector of insertion values (strings to insert) as second item. Note that the insertion indices are matched to the insertion values from left to right. Therefore, the number of insertion indices must equal the number of insertion values. The insertion values can be multi character strings.
